Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-02 paper/paper.tex
misc revision

\begin{itemize}
  \item If the closure set is an empty set (@Nil@ in the code since we list to represent that set),
then we have tried all the closures of this fork point and should move to the
next fork point. Since the meta-continuation @nkd@ is represented by a list, and we always
append new elements to its front, we are resuming to the most recent fork point by
popping up the front-most element and using the tail of that list.
  \item Otherwise, we pop a closure from the set, then build a new
environment and a new store for the body expression of the closure;
we use the same frame list and time that are copied from the fork point rather
than current one.
The meta-continuation @new_ndk@ is also updated by the removal of that closure, which makes
sure we will eventually shrink to the empty set case.
\end{itemize}

>>>>

\begin{itemize}
  \item If the closure set is an empty set (@Nil@ in the code since we use list to represent that set),
then we have tried all the closures of this fork point and should move to the
next fork point. Since the meta-continuation @nkd@ is represented by a list, and we always
append new elements to its front, we are resuming to the most recent fork point by
popping up the front-most element and using the tail of that list.
  \item Otherwise, we pop a closure from the set, then build a new
environment and a new store for the body expression of that closure.
We use the same frame list and time which are copied from the fork point rather
than current one.
The meta-continuation @new_ndk@ is also updated by the removal of that popped closure, which makes
sure the closure set will eventually shrink to empty.
\end{itemize}
